---
title: "P8105_hw2"
author: "yz4188"
date: 2021-10-08
output: github_document
---

```{r setup}
library(tidyverse)
library(readxl)
library(dplyr)
library(ggplot2)
library(janitor)
```



### Problem 1
## Read and clean the Mr. Trash Wheel sheet
```{r}
TrashWheel_df = read_excel("data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx",
  sheet = "Mr. Trash Wheel", range = cell_cols("A:N")) %>% 
janitor::clean_names() %>% 
drop_na(dumpster) %>% 
mutate(sports_balls = round(sports_balls))

```

## Read and clean precipitation data for 2018 and 2019

```{r Problem 1}
precipitation2018_df = read_excel("data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx", 
  sheet = "2018 Precipitation", skip = 1) %>% 
janitor::clean_names() %>% 
drop_na(month) %>% 
mutate(year = 2018, month = month.name) 

precipitation2019_df = read_excel("data/Trash-Wheel-Collection-Totals-7-2020-2.xlsx", 
  sheet = "2019 Precipitation", skip = 1) %>% 
janitor::clean_names() %>% 
drop_na(month) %>% 
mutate(year = 2019, month = month.name) 
```

####Conclusions for this problem 1
For "TrashWheel_df" observations is the "nrow(TrashWheel_df)" 
For "precipitation2018_df" observations is"nrow(precipitation2018_df)" 
For "precipitation2019_df" observations is "nrow(precipitation2019_df)" 
For "total precipitation in 2018" is "sum(pull(precipitation2018_df, total))"  
For "median number of sports balls in a dumpster in 2019" is "median(pull(TrashWheel_df,sports_balls))"



### Problem 2
```{r Problem 2}
pols_data = read_csv("data/pols-month.csv") %>% 
separate(col = mon, into = c("year", "month", "day")) %>% 
mutate(year = as.character(year), 
       month = as.integer(month),
       month = month.name[month],
president = ifelse(prez_dem =="1","dem","gop")) %>% 
select(-prez_dem, -prez_gop, -day) 

snp_data = read_csv("data/snp.csv") %>% 
mutate(date = lubridate::mdy(date)) %>%
separate(col = date, into = c("year", "month", "day")) %>% 
mutate(year = as.numeric(year),
       year = ifelse(year > 2021, year - 100, year)) %>% 
       arrange(year,month) %>% 
mutate(year = as.character(year),
       month = as.integer(month),
       month = month.name[month]) %>%
select(-day)

unemployment_data = read_csv("data/unemployment.csv") %>% 
     pivot_longer(Jan:Dec,
                 names_to = "month",
                 values_to = "unemployment_percentage") %>%
    mutate(Year = as.character(Year),
           month = match(month,month.abb),
           month = month.name[month]) %>%
    rename(year = Year) %>%
    relocate(year, month) %>% 
    arrange(year,month)

result_data= left_join(left_join(pols_data,snp_data),unemployment_data)
```

##**pols_data**
The dimension is "nrow(pols_data)" x " ncol(pols_data)". 
The range of this data is "min(range(pull(pols_data,year))): max(range(pull(pols_data,year)))". 
The names of key variables: " names(pols_data)".

##**snp_data**

The dimension is "nrow(snp_data)" "ncol(snp_data)". 
Then range of this data is "min(range(pull(snp_data ,year))) : max(range(pull(snp_data ,year)))"
The names of key variables: " names(snp_data)".

**unemployment_data**
The dimension is "nrow(unemployment_data)" "ncol(unemployment_data)". 
Then range of this data is "min(range(pull(unemployment_data ,year))) : max(range(pull(unemployment_data ,year)))"
The names of key variables: " names(unemployment_data)".

**result_data**
The dimension is "nrow(result_data)" "ncol(result_data)". 
Then range of this data is "min(range(pull(unemployment_data ,year))) : max(range(pull(unemployment_data ,year)))"
The names of key variables: " names(unemployment_data)".



## Problem 3
```{r}
name = read.csv("data/Popular_Baby_Names.csv") %>%
distinct()%>%
select(Year.of.Birth, Gender, Ethnicity, Child.s.First.Name, Rank) %>%
filter(Gender == "FEMALE", Child.s.First.Name == "Olivia")
name


name = read.csv("data/Popular_Baby_Names.csv") %>%
distinct()%>%
select(Year.of.Birth, Gender, Ethnicity, Child.s.First.Name, Rank) %>%
filter(Gender == "MALE", Rank == 1) 
name

name = read.csv("data/Popular_Baby_Names.csv") %>%
distinct()%>%
select(Year.of.Birth, Gender, Ethnicity, Child.s.First.Name, Rank, Count) %>%
filter(Gender == "MALE", Ethnicity == "WHITE NON HISPANIC", Year.of.Birth == 2016) 
name
ggplot(name, aes(x = Count, y = Rank)) + geom_point()
```

